### 2016-03-01 tex/toy.tex
Initial refactor. Nothing works at the moment, but want to get something committed.

>>>>

\section{Adding Complexity}
\subsection{SALT2 Model for Transient Luminosity}
The SALT2 model for supernova luminosity as a function of SN-frame time $t$  and wavelength $\lambda$ is
\begin{equation}
L(t-t_0, \lambda; M-x_0-\alpha x_1 + \beta c, x_1, c),
\label{SALTL:eqn}
\end{equation}
where $\alpha$ and $\beta$ are global parameters and $t_0$, $x_0$, $x_1$ and $c$ are per-supernova parameters.

Incorporating the SALT2 model leads to changes to the PGM in Figure~\ref{pgm:fig}, specifically in the following Nodes.
UNITY notation and priors are taken.
\subsubsection{SNX Luminosity}
There are parameters for the global supernova parameters.  For SNe~Ia
\begin{align}
M_{SNIa} & \sim \mathcal{U}(-20, -18) \\
\arctan{\alpha_{SNIa}} & \sim \mathcal{U}(-0.2, 0.3) \\
\arctan{\beta_{SNIa}} & \sim \mathcal{U}(-1.4, 1.4)
\end{align}
and for ``hyperparameters'' that describe the distributions of the per-supernova parameters
\begin{align}
\log_{10}{R^{x_0}_{SNIa}} & \sim \mathcal{U}({-2}, {-0.5})\\
\log_{10}{R^{x_1}_{SNIa}} & \sim \mathcal{U}({-0.5}, {0.5})\\
\log_{10}{R^{c}_{SNIa}} & \sim \mathcal{U}({-1.5}, {-0.5})\\
x_{1,SNIa}^\star& \sim \text{Cauchy}(0,1)\\
c^\star_{SNIa} & \sim \text{Cauchy}(0,0.3).
\end{align}

\subsubsection{Type}
The type of the object is still obtained as before.  Now we have the parameters that specify the sub-type.
\begin{align}
t_0 & \sim \mathcal{U}\\
x_{0, SNIa} & \sim \mathcal{N}(0,R^{x_0}_{SNX})\\
x_{1,SNIa} & \sim \mathcal{N}(x_{1,SNIa}^\star,R^{x_1}_{SNIa})\\
c_{SNIa} & \sim \text{SkewNormal}(c^\star_{SNIa},R^{c}_{SNIa} )
\end{align}

\subsubsection{Luminosity}
The luminosity is now fixed by Eqn.\ \ref{SALTL:eqn}.  It may be made probabilistic if an error snake is considered.

\subsubsection{Likelihood}
The likelihood for typed objects is
\begin{multline}
\mathcal{L}(T_o,z_o,c_o | S_c, S_T, z, X)
 \propto \int dt_0 \, dx_{0,T_o} \, dx_{1,T_o} dc_{T_o} 
 p(t_0, x_{0,T_o}, x_{1,T_o}, c_{T_o} |T_o, z=z_o, X) \\ P(T_o|z=z_o, X) p(c_o, S_c, S_T | T=T_o, L_{T_o}(t_0, x_{0,T_o}, x_{1,T_o}, c_{T_o}), z=z_o, X)
\end{multline}
and for non-typed
\begin{multline}
\mathcal{L}(z_o,c_o | S_c, S_T, z, X)
 \propto \sum_j p_j \sum_i P(T_i|z=z_j, X)   \int dt_0 \, dx_{0,T_i} \, dx_{1,T_i} dc_{T_i} 
 p(t_0, x_{0,T_i}, x_{1,T_i}, c_{T_i} |T_i, z=z_j, X) \\  p(c_o, S_c, S_T | T=T_o, L_{T_i}(t_0, x_{0,T_i}, x_{1,T_i}, c_{T_i}), z=z_j, X),
 \end{multline}
where both likelihoods must be normalized.
